Work Day

### 2013-08-10 sandbox/pbc-workday/2013-08.tex
August workday.

\documentclass[12pt]{article}
\newcommand{\BI}{\begin{enumerate}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{enumerate}}
\title{Work Day}
\begin{document}
\maketitle
Items are listed in order of \emph{approximate} priority. 
\BI Main Sanctuary
    \BI Vacuum pews and carpet
    \I  General cleaning (remove old bulletins...) \EI
\I  Unplug Annex toilet.
    \BI Toilet may need to be completely removed 
        and then re-installed if conventional unplugging methods fail. \EI
\I  Bathrooms: Regular cleaning and restocking
\I  Maintenance of the AC system for the sanctuary.
    \BI Main AC system is the one that is ``tucked away'' in the attic,
        \emph{not} the first one that you see when you go up there.
    \I  New filters need to be installed, they are on top of the other AC system. 
    \I  Also, attempt to find and fix the cause of the condensation
        which is leaking through to the foyer. \EI
\I  Purchase and install rubber ring-boots for vent flashings 
    (pipes sticking out of roof) near the roof by the main entrance 
    of the main building.
    \BI Diameter of pipes (flashings) and approximate degree of roof 
        need to first be measured in order to purchase the correct rubber boots.
    \I  Rubber boots then need to be installed. \EI
\I  Annex
    \BI Sweep floors
    \I  Clean and restock bathroom (including better solution for hand soap) \EI
\I  Water heater in main building
    \BI Purchase and install seismic restraint for the water heater 
        of the main building
    \I  Purchase and install piping in order to route 
        the Temperature/Pressure Relief valve (TPR valve) of the water heater 
        to the adjacent floor sink. \EI
\I  Electrical Panel for main building
    \BI The electrical panel (located “around the corner” from main entrance) 
        has openings in it, which need to be covered. \EI
\I  Park strips
    \BI Check the park strips both at the front and back of the church 
        for weeds and litter. \EI
\I  Roof gutters in main building
    \BI Clean gutters of debris \EI
\EI
\end{document}

>>>>

\documentclass[12pt]{article}
\newcommand{\BI}{\begin{enumerate}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{enumerate}}
\title{Work Day}
\begin{document}
\maketitle
Items are listed in order of \emph{approximate} priority. 
\BI Main Sanctuary
    \BI Vacuum pews and carpet
    \I  Restock visitor cards and pencils into pews.
    \I  General cleaning (remove old bulletins...) \EI
\I  Bathrooms: Regular cleaning and restocking
\I  Annex carpet estimate 
    \BI We haven't committed to carpeting the Annex, 
        but it would be really beneficial to have a cost/work/style estimate.
    \I  If unexperienced with carpeting rooms, you may want to consult someone
        who does or the internet first.
    \I  Determine amount of carpeting needed to cover annex dining room.
    \I  Visit Lowe's (811 E Arques Ave) and choose around 3 carpet samples.
    \I  Also, obtain cost estimates for each of the samples.
    \I  Hopefully we can plan on a carpet to install next month. \EI
\I  General restocking of needed items
\I  Re-organize the janitor closet
    \BI Feel free to throw away what does not appear useful
        (e.g. bottles with only a little solution remaining). \EI
\I  Annex
    \BI Sweep floors
    \I  Clean and restock bathroom (including better solution for hand soap) \EI
\I  General outdoor cleaning
    \BI Leaves in front of main church entryway.
    \I  General weeding in the lawn area between the main building and annex. \EI
\I  Annex soundproofing
    \BI Research creative, cost-efficient ways to add soundproofing to the
        Annex dining room. \EI
\I  Remove or grind down the metal peice protruding from Annex.
\I  Purchase and install rubber ring-boots for vent flashings 
    (pipes sticking out of roof) near the roof by the main entrance 
    of the main building.
    \BI Diameter of pipes (flashings) and approximate degree of roof 
        need to first be measured in order to purchase the correct rubber boots.
    \I  Rubber boots then need to be installed. \EI
\I  Finish trimming hedges around the parking lot. 
\EI
\end{document}
